Longitudinal Principal Manifold Estimation

### 2023-12-15 paper/main.tex
paper updates

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.4]{sim_case1_plot2}
  \caption{Longitudinal Simulated Data with $D = 2$. Data from the function ADD FUNCTION are simulated at 5 time points. Random noise is added both in time and space as ADD FUNCTION.}
  \label{fig:sample_data}
\end{figure}

Assume that our goal is estimation of a smooth surface for the brain region of interest at each time point such that the changes of the surface over time are smooth. It is important for the resulting manifolds to be estimated at each time point in order to enable further inference, i.e. modeling trajectories of change in region volumes over time, identifying regions that are most affected in terms of atrophy, etc. The key reasons why the existing principal manifold estimation methods cannot be implemented in this setting are 1) if we implement the data reduction method above then the resulting principal manifold will not be a function of time $t_j$ which is necessary for the resulting segmentations to be useful in practice, 2) if the manifold is estimated separately at each time point, the results may not be smooth over time. In other words, the dimension reduction should be implemented to obtain the 2-dimensional coordinates $(y_1,y_2,t_j)$ while ensuring that the resulting manifold is also a function of $t_j$. In order to address the limitations of the existing approaches for the setting described above, we now propose longitudinal principal manifold estimation (LPME) algorithm to estimate $d$-dimensional representations of $D$-dimensional objects observed over time.

@@

Given the framework proposed in the previous Section, estimation of the longitudinal principal manifold entails minimizing the function in (\ref{eq:newKappa}). Our proposed algorithm is based on a multi-stage approach, where we consider smoothing of the data clouds at each time point (spatial smoothing) and then smoothing of the obtained manifolds over time (temporal smoothing).At each individual time point we assume that a manifold has been fit to the data cloud using a spline-based mapping. Hence, in the spatial smoothing phase we assume that we have a collection of spline coefficients that can be used to project from the low-dimensional parameterization to the high-dimensional space. For example, the PME algorithm can be used to obtain this parameterization. In the LPME algorithm, we then use these low-dimensional representations at each time point as the outcomes in a thin plate spline, thus smoothing over the spatial spline coefficients with respect to time. This yields a multi-stage model that, for a provided time point and set of tuning parameters, obtains a set of spline coefficients that are time-dependent, then returns the high-dimensional output of the spline function associated with the tuning parameter set. Our proposed LPME algorithm consists of four steps: data reduction, initialization, fitting, and tuning. A visualization of these steps is shown in Figure \ref{fig:lpme_steps}. Details of this approach are described below, and an implementation is available as an \texttt{R} package at \texttt{https://github.com/rjzielinski/pme}.

@@

The next step in developing the algorithm for estimation of the longitudinal principal manifold is initialization. Different algorithms use different approaches for this step. For example, the PME algorithm uses Isomap (\cite{tenenbaumGlobalGeometricFramework2000}) to develop an initial parameterization, which the algorithm proceeds to iteratively improve. However, implementation of commonly used approaches for initialization in our setting can be problematic. For instance, using ISOMAP to find parameterizations of similarly shaped structures (i.e. the brain region of interest at each time point) is likely to result in inconsistent parameterization directions (i.e. low values in the parameter space may be associated with low values in the embedding space for one run, while low values in the parameter space may be associated with high values in the embedding space in another). This is demonstrated in Figure \ref{fig:inconsistent_parameterization} which shows differences in parameterizations depending on the time points of the data cloud presented in Figure \ref{fig:sample_data}. Reaching a successful fit in the LPME algorithm requires consistent parameterizations across time points, so a different approach to generating an initial parameterization is needed.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{inconsistent_parameterization}
  \caption{Simulated Data with Inconsistent Parameterization}
  \label{fig:inconsistent_parameterization}
\end{figure}

To obtain the same parameterization of the manifold over time, instead of using Isomap at each time point separately, we propose collapsing the time dimension in the cluster centers of all time steps, then using one Isomap run to reach a parameterization for the centers across all time points simultaneously. This approach is based on the assumption that the shape of the structure, i.e. the brain region of interest, remains relatively stable over time. In Section \ref{s:simulations}, we consider some deviations from this assumption and their effect on the results and we show that this process ensures that the initial parameterization remains consistent over time under the assumption of relative stability of the shape of the structure.

@@

Once the initial parameterization for each cluster center is obtained, the model fitting process begins by using this parameterization as the initialization for runs of the PME algorithm at each time point. Specifically, for each time point, the cluster centers associated with the given time value, their weights, and the corresponding parameterizations for these points are used to initialize a PME run. This results in an estimated principal manifold $\widehat{f_t}$ for each time point $t$ and an optimal tuning parameter $\lambda_t^*$ corresponding to the first two terms of the $\mathcal{K}_{\lambda, \gamma, \mathbb{P}}(F)$ defined in ~\eqref{eq:newKappa} and presented using multicolored lines in Figure \ref{fig:lpme_steps} (c). At this stage, the time-specific manifolds require further smoothing considering the curvature in the time dimension corresponding to the third term of $\mathcal{K}_{\lambda, \gamma, \mathbb{P}}(F)$. The principal manifold $\widehat{f_t}$ at time $t$ is characterized by spline coefficients. Hence, we estimate a spline function mapping from the time dimension to the coefficient space that smooths over the coefficients for these principal manifolds, given a tuning parameter $\gamma$.

At each time point, the estimated principal manifold has a spline form. As detailed by \cite{greenSilverman1994}, splines can be considered to have knots at the points used to fit them. This means that, in order for the coefficients of the manifolds estimated at each time point to be comparable, the parameter values used as inputs when the functions were fitted must be identical. Hence, to obtain coefficients that can be compared across time points, a grid of values $\left\{\boldsymbol{r}_i\right\}_{i=1}^{N}$ ($\subset\mathbb{R}^d$) ranging from the minimum to the maximum of the parameters in each of the $d$ dimensions is input into the estimated embedding functions $\widehat{f_t}$ for each time point, with $N$ specified based on the maximum number of clusters identified in the data reduction step at any time point. This yields a set of outcomes, $\left\{Y_{i,t}\right\}_{i=1, t = 1}^{N, T}$, corresponding to same parameter values at each time point, i.e., $Y_{i,t}=\widehat{f_t}(\boldsymbol{r}_i)$ for all $i$ and $t$. Following the discussion in Chapter 7 of \cite{greenSilverman1994}, for each time point $t$, comparable spline coefficients $\boldsymbol{s}_t^*$ and $\boldsymbol{\alpha}_t^*$ can then be calculated by minimizing the following function.
\begin{equation}\label{eq:splineL}
    \mathcal{L}(f_t) = (\boldsymbol{Y}_t - \boldsymbol{E}\boldsymbol{s}_t - \boldsymbol{R}^\T\boldsymbol{\alpha}_t)^\T(\boldsymbol{Y}_t - \boldsymbol{E}\boldsymbol{s}_t - \boldsymbol{R}^\T\boldsymbol{\alpha}_t) + \gamma\boldsymbol{s}_t^\T \boldsymbol{E}\boldsymbol{s}_t
\end{equation}    
where $\boldsymbol{Y}_t$ is the $N \times N$ matrix consisting of elements $\left\{Y_{i,t}\right\}_{i=1}^{N}$ at each time point $t$, the matrix $\boldsymbol{E}=(E_{ij})_{1\le i,j\le N}$ is defined by $E_{ij} = \eta_{d}(\|\boldsymbol{r}_i - \boldsymbol{r}_j\|)$, where $\eta_{d}(r) = r^{4 - d}\log r$ if $d$ is even, and $\eta_d(r) = r^{4-d}$ if $d$ is odd, the functions $\phi_1,\ldots,\phi_{d+1}$ form a basis of the linear space of polynomials on $\mathbb{R}^d$ with degrees $\le1$; and the matrix $\boldsymbol{R}=(R_{ij})_{1\le i\le d+1,1\le j\le N}$ is defined by $R_{ij} = \phi_i(\boldsymbol{r}_j)$.

@@

We denote the manifold coefficients at each time point $t$ as $\boldsymbol{\omega}_t = (\boldsymbol{s}_t^{*\T}, \boldsymbol{\alpha}_t^{*\T})^\T$. To limit the ability of a poorly-fitting PME estimate to greatly influence the results of the LPME model, we fit a weighted spline model to smooth over the manifold coefficients, where $\tau_t$ denote the estimated mean squared distance of the PME model fit at time $t$, the weights for each time are equal to 
$$w_t = \frac{1}{\tau_t\sum_{i=1}^{T}\frac{1}{\tau_i}}.$$

@@

  Apply Isomap to parameterize $\left\{\mu_{j, t}\right\}_{j = 1, t = 1}^{N_t, T}$ by the $d$-dimensional parameters $\left\{r_{j, t}\right\}_{j = 1, t = 1}^{N_t, T}$. Formally set $\pi_{f_t(0)}(\mu_{j, t}) \gets r_{j, t}$ for $j = 1, 2, \dots, N_t$, $t = 1, 2, \dots, T$\;

@@

Notably, in many applications where manifold learning is implemented, the high-dimensional shapes of interest are self-intersecting manifolds. Methods based on the principal curve framework, including the principal manifold approach used here, are typically unable to fit such manifolds due to the self-consistency property. To avoid this issue, we propose a data augmentation approach with polar or spherical coordinates, depending on the value of $D$. As a simple example, the unit circle can be considered a self-intersecting manifold with $d = 1$ when viewed in two dimensions. However, by adding a third dimension equal to the angle of each observation from the origin, the manifold can be considered as having $d = 1$ and $D = 3$, while avoiding any self-intersections. This enables the PME algorithm, and thus the LPME algorithm, to be fit under these circumstances. This process is illustrated graphically in Figure \ref{fig:unit_circle_augmentation}.

@@

Visualizations of the results from some of the simulation cases, truncated for concision to include only integer-valued time points, are shown in Figures \ref{fig:sim_case1}, \ref{fig:sim_case4} and \ref{fig:sim_case6}. Informally, the performance of each estimation method can be observed by considering the proximity of each method's estimated manifold to the true manifold (shown in red) over time. Thus, in Figure \ref{fig:sim_case1}, we see that the LPME-estimated manifold bears the closest resemblance to the true manifold underlying the data, while the manifolds estimated by PME and the principal curve method show greater responses to temporary random fluctuations in the data at each time point.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Case & Data & LPME & PME & PC/PS \\
    \hline
    1 & 0.146 (0.233) & 0.074 (0.122) & 0.131 (0.258) & 0.118 (0.206) \\
    2 & 0.467 (0.665) & 0.248 (0.516) & 0.516 (0.750) & 0.564 (0.419) \\
    3 & 0.291 (0.601) & 0.239 (0.564) & 0.317 (0.640) & 0.264 (0.584) \\
    4 & 4.26 (21.2) & 3.29 (13.0) & 4.23 (21.1) & 4.22 (21.2) \\
    5 & 0.895 (1.33) & 0.584 (1.08) & 0.894 (1.36) & 0.821 (1.22) \\
    6 & 0.284 (1.06) & 0.273 (0.891) & 0.316 (1.04) & 0.557 (0.387) \\
    7 & 0.145 (0.552) & 2.96 (4.65) & 6.92 (1.17) & 1.58 (0.514) \\
    8 & 0.110 (0.325) & 0.074 (0.208) & 0.115 (0.331) & 0.172 (0.234) \\
    \hline
  \end{tabular}
  \caption{MSD Comparison to True Values, Median (IQR).}
  \label{table:simulation_results_median}
\end{table}

@@

@@

Another limitation stems from the performance of the LPME method on the hippocampus surfaces obtained from the ADNI dataset. It is clear that neither the PME nor the LPME estimates were able to fully capture the distinctive curved structure of the hippocampus. This shortcoming could potentially be addressed in several ways. First, as discussed above, the manifold learning method used in the initialization step of the PME algorithm, or the parameters of that method could be adjusted to better meet the needs of the specific manifold being estimated. Second, while a simple grid search is used to select the optimal value of the smoothing parameter in both the PME and LPME algorithms, it is possible that an improved search method would yield results that are more sensitive to the nuances of the structure being estimated. Finally, it may be possible to manipulate the manifold to be easier to estimate through adjustments to the data augmentation process, as described in Section 4.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.4]{sim_case1_plot2}
  \caption{Longitudinal Simulated Data with $D = 2$. Data from the functions $x_1 = r$ and $x_2 = \alpha\sin(\beta r + \frac{\pi}{2})$ are simulated at 5 time points. Random noise is added both in time and space as $\zeta \mathbf{g}(t) + \iota$, where $\mathbf{g}(t)$ represents a normally distributed spatial translation applied to all points at each time point, and $\iota$ represents normally distributed noise applied to each point individually.}
  \label{fig:sample_data}
\end{figure}

Assume that our goal is estimation of a smooth surface for the brain region of interest at each time point such that the changes of the surface over time are smooth. It is important for the resulting manifolds to be estimated at each time point in order to enable further inference, i.e. modeling trajectories of change in region volumes over time, identifying regions that are most affected in terms of atrophy, etc. The key reasons why the existing principal manifold estimation methods cannot be implemented in this setting are 1) if we implement the data reduction method above then the resulting principal manifold will not be a function of time $t_j$, which is necessary for the resulting segmentations to be useful in practice, 2) if the manifold is estimated separately at each time point, the results may not be smooth over time. In other words, the dimension reduction should be implemented to obtain the 2-dimensional coordinates $(y_1,y_2,t_j)$ while ensuring that the resulting manifold is also a function of $t_j$. In order to address the limitations of the existing approaches for the setting described above, we now propose longitudinal principal manifold estimation (LPME) algorithm to estimate $d$-dimensional representations of $D$-dimensional objects observed over time.

@@

Given the framework proposed in the previous Section, estimation of the longitudinal principal manifold entails minimizing the function in (\ref{eq:newKappa}). Our proposed algorithm is based on a multi-stage approach, where we consider smoothing of the data clouds at each time point (spatial smoothing) and then smoothing of the obtained manifolds over time (temporal smoothing). At each individual time point we assume that a manifold has been fit to the data cloud using a spline-based mapping. Hence, in the spatial smoothing phase we assume that we have a collection of spline coefficients that can be used to project from the low-dimensional parameterization to the high-dimensional space. For example, the PME algorithm can be used to obtain this parameterization. In the LPME algorithm, we then use these low-dimensional representations at each time point as the outcomes in a thin plate spline, thus smoothing over the spatial spline coefficients with respect to time. This yields a multi-stage model that, for a provided time point and set of tuning parameters, obtains a set of spline coefficients that are time-dependent, then returns the high-dimensional output of the spline function associated with the tuning parameter set. Our proposed LPME algorithm consists of four steps: data reduction, initialization, fitting, and tuning. A visualization of these steps is shown in Figure \ref{fig:lpme_steps}. Details of this approach are described below, and an implementation is available as an \texttt{R} package at \texttt{https://github.com/rjzielinski/pme}.

@@

The next step in developing the algorithm for estimation of the longitudinal principal manifold is initialization. Different algorithms use different approaches for this step. For example, the PME algorithm uses Isomap (\cite{tenenbaumGlobalGeometricFramework2000}) to develop an initial parameterization, which the algorithm proceeds to iteratively improve. However, implementation of commonly used approaches for initialization without considering the nuances posed by longitudinal data can be problematic. For instance, using ISOMAP to find parameterizations of similarly shaped structures (i.e. the brain region of interest at each time point) is likely to result in inconsistent parameterization directions across time points (i.e. low values in the parameter space may be associated with low values in the embedding space for one run, while low values in the parameter space may be associated with high values in the embedding space in another). This is demonstrated in Figure \ref{fig:inconsistent_parameterization}, which shows differences in parameterizations depending on the time points of the data cloud presented in Figure \ref{fig:sample_data}. Reaching a successful fit in the LPME algorithm requires consistent parameterizations across time points, so a different approach to generating an initial parameterization is needed.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{inconsistent_parameterization}
  \caption{Simulated data with $D = 2$. The curves shown in this plot represents embedding maps estimated by PME for each time point, with time indicated by the color of the curve. The $X$ and $Y$ axes represent the coordinates of the curve in $D$-dimensional space, while $R$ represents the estimated parameters associated with these coordinates. Randomness in the initialization of the PME algorithm may result in misaligned parameterizations of the estimated embedding maps, as seen at two time points.}
  \label{fig:inconsistent_parameterization}
\end{figure}

To obtain the same parameterization of the manifold over time, instead of using Isomap at each time point separately, we propose using PME to develop a parameterization of the data taken from the first time point, then using the projection index associated with this estimate to find initial parameterizations of the centers for the remaining time points. This approach is based on the assumption that the shape of the structure, i.e. the brain region of interest, remains relatively stable over time. In Section \ref{s:simulations}, we show that this process ensures that the initial parameterization remains consistent over time under the assumption of relative stability of the shape of the structure, and we consider some deviations from this assumption and their effect on the results.

@@

Once the initial parameterization for each cluster center is obtained, the model fitting process begins by using the cluster centers, weights and parameterizations associated with each time point to initialize a PME run. This results in an estimated principal manifold $\widehat{f_t}$ for each time point $t$ and an optimal tuning parameter $\lambda_t^*$ corresponding to the first two terms of the $\mathcal{K}_{\lambda, \gamma, \mathbb{P}}(F)$ defined in \eqref{eq:newKappa} and presented using multicolored lines in Figure \ref{fig:lpme_steps} (c). The fit of each $\hat{f}_t$ is measured using $\tau_t$, an estimate of the mean squared distance between the observed data points and their projections to the manifold defined by $\hat{f}_t$. At this stage, the time-specific manifolds require further smoothing considering the curvature in the time dimension corresponding to the third term of $\mathcal{K}_{\lambda, \gamma, \mathbb{P}}(F)$. The principal manifold $\widehat{f_t}$ at time $t$ is characterized by spline coefficients. Hence, we estimate a spline function mapping from the time dimension to the coefficient space that smooths over the coefficients for these principal manifolds, given a tuning parameter $\gamma$.

At each time point, the estimated principal manifold has a spline form. As detailed by \cite{greenSilverman1994}, smoothing splines can be considered to have knots at the points used to fit them. This means that, in order for the coefficients of the manifolds estimated at each time point to be comparable, the parameter values used as inputs when the functions were fitted must be identical. Hence, to obtain coefficients that can be compared across time points, a grid of values $\left\{\boldsymbol{r}_i\right\}_{i=1}^{N}$ ($\subset\mathbb{R}^d$) ranging from the minimum to the maximum of the parameters in each of the $d$ dimensions is input into the estimated embedding functions $\widehat{f_t}$ for each time point, with $N$ specified based on the maximum number of clusters identified in the data reduction step at any time point. This yields a set of outcomes, $\left\{Y_{i,t}\right\}_{i=1, t = 1}^{N, T}$, corresponding to same parameter values at each time point, i.e., $Y_{i,t}=\widehat{f_t}(\boldsymbol{r}_i)$ for all $i$ and $t$. Following the discussion in Chapter 7 of \cite{greenSilverman1994}, for each time point $t$, comparable spline coefficients $\boldsymbol{s}_t^*$ and $\boldsymbol{\alpha}_t^*$ can then be calculated by minimizing the following function.
\begin{equation}\label{eq:splineL}
    \mathcal{L}(f_t) = (\boldsymbol{Y}_t - \boldsymbol{E}\boldsymbol{s}_t - \boldsymbol{R}^\T\boldsymbol{\alpha}_t)^\T(\boldsymbol{Y}_t - \boldsymbol{E}\boldsymbol{s}_t - \boldsymbol{R}^\T\boldsymbol{\alpha}_t) + \gamma\boldsymbol{s}_t^\T \boldsymbol{E}\boldsymbol{s}_t
\end{equation}    
where $\boldsymbol{Y}_t$ is the $N \times N$ matrix consisting of elements $\left\{Y_{i,t}\right\}_{i=1}^{N}$ at each time point $t$, the matrix $\boldsymbol{E}=(E_{ij})_{1\le i,j\le N}$ is defined by $E_{ij} = \eta_{d}(\|\boldsymbol{r}_i - \boldsymbol{r}_j\|)$, where $\eta_{d}(r) = r^{4 - d}\log r$ if $d$ is even, and $\eta_d(r) = r^{4-d}$ if $d$ is odd, the functions $\phi_1,\ldots,\phi_{d+1}$ form a basis of the linear space of polynomials on $\mathbb{R}^d$ with degrees $\le1$; and the matrix $\boldsymbol{R}=(R_{ij})_{1\le i\le d+1,1\le j\le N}$ is defined by $R_{ij} = \phi_i(\boldsymbol{r}_j)$.

@@

We denote the manifold coefficients at each time point $t$ as $\boldsymbol{\omega}_t = (\boldsymbol{s}_t^{*\T}, \boldsymbol{\alpha}_t^{*\T})^\T$. To limit the ability of a poorly-fitting PME estimate to greatly influence the results of the LPME model, we fit a weighted spline model to smooth over the manifold coefficients, where the weights for each time point $t$ are equal to 
$$w_t = \frac{1}{\tau_t\sum_{i=1}^{T}\frac{1}{\tau_i}}.$$

@@

  Apply PME to parameterize $\left\{\mu_{j, 1}\right\}_{j = 1}^{N_1}$ by the $d$-dimensional parameters $\left\{r_{j, t}\right\}_{j = 1}^{N_1}$ and use $\pi_{f_1(0)}$ to parameterize $\left\{\mu_{j, t}\right\}_{j=1, t = 1}^{N_t, T}$ by $\left\{r_{j, t}\right\}_{j=1, t=2}^{N_t, T}$. Formally set $\pi_{f_1(0)}(\mu_{j, 1}) \gets r_{j, 1}$ for $j = 1, 2, \dots, N_1$, and $\pi_{f_{t}(0)}(\mu_{j, t}) \gets \pi_{f_1(0)}(\mu_{j, t})$ for $j = 1, 2, \dots, N_t$, $t = 2, \dots, T$\;

@@

Notably, in many applications where manifold learning is implemented, the high-dimensional shapes of interest are self-intersecting manifolds. Methods based on the principal curve framework, including the principal manifold approach used here, are typically unable to fit such manifolds due to the self-consistency condition. To avoid this issue, we propose a data augmentation approach with polar or spherical coordinates, depending on the value of $D$. As a simple example, the unit circle can be considered a self-intersecting manifold with $d = 1$ when viewed in two dimensions. However, by adding a third dimension equal to the angle of each observation from the origin, the manifold can be considered as having $d = 1$ and $D = 3$, while avoiding any self-intersections. This enables the PME algorithm, and thus the LPME algorithm, to be fit under these circumstances. This process is illustrated graphically in Figure \ref{fig:unit_circle_augmentation}.

@@

Visualizations of the results from some of the simulation cases, truncated for concision, are shown in Figures \ref{fig:sim_case1} and \ref{fig:sim_case6}. Informally, the performance of each estimation method can be observed by considering the proximity of each method's estimated manifold to the true manifold (shown in red) over time. Thus, in Figure \ref{fig:sim_case1}, we see that the LPME-estimated manifold bears the closest resemblance to the true manifold underlying the data, while the manifolds estimated by PME and the principal curve method show greater responses to temporary random fluctuations in the data at each time point.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c c c c c|}
    \hline
    Case & Data & LPME & PME & PC/PS \\
    \hline
    1 & 0.146 (0.233) & {\bf 0.074 (0.122)} & 0.131 (0.258) & 0.118 (0.206) \\
    2 & 0.467 (0.665) & {\bf 0.248 (0.516)} & 0.516 (0.750) & 0.564 (0.419) \\
    3 & 0.291 (0.601) & {\bf 0.239 (0.564)} & 0.317 (0.640) & 0.264 (0.584) \\
    4 & 4.26 (21.2) & {\bf 3.29 (13.0)} & 4.23 (21.1) & 4.22 (21.2) \\
    5 & 0.895 (1.33) & {\bf 0.584 (1.08)} & 0.894 (1.36) & 0.821 (1.22) \\
    6 & 0.284 (1.06) & {\bf 0.273 (0.891)} & 0.316 (1.04) & 0.557 (0.387) \\
    7 & 0.145 (0.552) & 2.96 (4.65) & 6.92 (1.17) & {\bf 1.58 (0.514)} \\
    8 & 0.110 (0.325) & {\bf 0.074 (0.208)} & 0.115 (0.331) & 0.172 (0.234) \\
    \hline
  \end{tabular}
  \caption{MSD comparison to true values, Median (IQR). The lowest algorithm-specific median (IQR) are highlighted in bold.}
  \label{table:simulation_results_median}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{}
\end{figure}

@@

Another limitation stems from the performance of the LPME method on the hippocampus surfaces obtained from the ADNI dataset. It is clear that neither the PME nor the LPME estimates were able to fully capture the distinctive curved structure of the hippocampus. This shortcoming could potentially be addressed in several ways. First, as discussed above, the manifold learning method used in the initialization step of the PME algorithm, or the parameters of that method could be adjusted to better meet the needs of the specific manifold being estimated. Second, while a simple grid search is used to select the optimal value of the smoothing parameter in both the PME and LPME algorithms, it is possible that an improved search method would yield results that are more sensitive to the nuances of the structure being estimated. Finally, it may be possible to manipulate the manifold to be easier to estimate through adjustments to the data augmentation process, as described in Section \ref{s:LPME}.
